\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 4 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

Numerical simulations performed in this section were conducted with the next-generation reservoir simulator IC-FERST model\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,jackson_2013,porosity_documentation,fluidity_manual}. This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{jackson_2015,pavlidis2016,salinas2015,salinas_2016,adam_2016b,su_2015,radunz_2014}.

>>>>

Numerical simulations were conducted with model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,jackson_2013,porosity_documentation,fluidity_manual}. This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{jackson_2015,pavlidis2016,salinas2015,salinas_2016,adam_2016b,su_2015,radunz_2014}.

All test-cases were performed in an idealised geometry discretised with unstructured triangular \PN[1]{2} and \PN[1]{1} FE mesh. In most simulations, the domain was initially fully saturated with the non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity ($u$). For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, i.e., $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$
